Distributed Range-Only Localisation that Preserves Sensor and Navigator Privacies

### 2022-03-03 authors_responses/conditional_accept/authors_response.tex
Continued on response. Few comments added for responses to reviewer two which are not yet written up nicely. Diff not yet updated

@@

@@

@@

@@

>>>>

This is a good question that had not been elaborated in the work. The key reason that any sensor-specific information (such as its measurement noise variance) is considered private is that it may hold identifying data if analysed by an adversary. For example, a particular model of sensor may be identified from its measurement noise variance, enabling a targeted attack (cyber or physical) against that sensor. We have made a change to the introduction section to clarify this reasoning.

@@

Thank you for pointing this out, we have added the change to the manuscript.

@@

My response.
abstraction from cryptography to capture the fact nothing is can be learnt from the encryptions

@@

My response.
Continuation from above. Since nothing is to be learnt, then any information from the navigator involved in the localisation must remain private. In practice, as is later evident from the concrete use of the scheme, the weights correspond to the navigator estimate which we want to hide from sensors

@@

My response.
Referenced on first use of the term. Was removed from appendix after previous reviews as fewer cryptographic background was requested by reviewers.

### 2022-03-03 main.tex
Added missing hyphen
Continued on response. Few comments added for responses to reviewer two which are not yet written up nicely. Diff not yet updated

Typical cryptographic secrecy involves hiding all transferred data such that external parties in the communication network learn no new information from acquired encryptions. This can be achieved with common symmetric and public-key encryption scheme such as AES \cite{gueronIntelAdvancedEncryption2010} and RSA \cite{rivestMethodObtainingDigital1978}, respectively. In some cases however, partial data leakage or encrypted data processing is required for achieving a desired goal which has led to several homomorphic and functional encryption schemes \cite{paillierPublicKeyCryptosystemsBased1999,shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013,chotardDecentralizedMultiClientFunctional2018} finding uses in signal processing or localisation tasks. In \cite{alanwarPrOLocResilientLocalization2017}, homomorphic encryption is used to make time-independent model-free location estimates where an estimator does not learn sensor measurements or locations. In \cite{aristovEncryptedMultisensorInformation2018}, similar secrecy is achieved with a linear Kalman filter when a hierarchical sensor network is present. In \cite{shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013}, privacy-preserving aggregation schemes are presented as a means to compute total powergrid usage without disclosing individual contributions, while in \cite{alexandruEncryptedCooperativeControl2019,alexandruPrivateWeightedSum2020}, centralised and hidden weighted sum aggregations, pWSAc and pWSAh, are introduced as a means for computing local control inputs in a distributed environment without learning individual inputs.

Our contribution in this work presents a range-only localisation method meeting formal cryptographic requirements that ensure sensors keep their measurements and locations private while the navigator keeps its estimates private. We first define a novel notion for private linear combination aggregation and present an implementation that satisfies these requirements, before using it to derive a filter based on the Extended Kalman Filter with no hierarchical sensor layout assumptions. The linear combination aggregation scheme we put forward is in principle similar to the pWSAh scheme in \cite{alexandruPrivateWeightedSum2020}, however, a formal definition with different communication assumptions and leakages is given, crucial for its cryptographic security. To the best of the authors' knowledge, no existing method for Bayesian state estimation using range-only sensors and meeting the desired privacy requirements exists.

We motivate this scenario with the example of vehicle localisation in the presence of privately owned measurement stations. While the intention of measurement stations is the accurate navigation of passing vehicles, it may be reasonable to desire identifying location or hardware details to remain unknown to the other present stations and the navigator. Similarly, a navigator may not wish to disclose their most accurate location estimates to untrusted third-party measurers.

@@

\section{Problem Statement} \label{sec:problem_statement}
In this work, we consider the context of privacy-preserving range sensor navigation, where we want no sensor to learn information about the navigator or other sensors beyond their local measurements, and the navigator to learn no information about individual sensors beyond its location estimate. The problem is two-fold, in that we require explicit cryptographic requirements with a suitable encryption scheme meeting them, as well as an estimation scheme that can use the scheme in the context of range-only navigation.

@@

As aggregation is typically performed on scalar inputs, we extend our notation to the context of multidimensional estimation data by letting an instance $t_{k,\tau}$ uniquely capture the scalar aggregation during an estimation timestep $k$ for a single element with position index $\tau$. To achieve this in practice, any injective function can be used, such as the concatenation $t_{k,\tau}=k\mathbin\|\tau$. The four algorithms defining our scheme are given as follows.
\begin{LaTeXdescription}
    \item[$\mathsf{Setup}(\kappa)$] On input parameter $\kappa$, generate two equal length, sufficiently large, primes $p$ and $q$, and compute $N=pq$. Define a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$, choose the number of weights to combine, $m>1$, and set public parameter $\mathsf{pub}=H$, navigator public key $pk_0 = N$ and navigator private key $sk_0=(p,q)$. Sensor secret keys are generated by choosing $sk_i,\,i\in\{1,\dots,n-1\}$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key as $sk_n = -\sum^{n-1}_{i=1}sk_i \pmod{N^2}$.

>>>>

Typical cryptographic secrecy involves hiding all transferred data such that external parties in the communication network learn no new information from acquired encryptions. This can be achieved with common symmetric and public-key encryption scheme such as AES \cite{gueronIntelAdvancedEncryption2010} and RSA \cite{rivestMethodObtainingDigital1978}, respectively. In some cases however, partial data leakage or encrypted data processing is required for achieving a desired goal which has led to several homomorphic and functional encryption schemes \cite{paillierPublicKeyCryptosystemsBased1999,shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013,chotardDecentralizedMultiClientFunctional2018} finding uses in signal processing or localisation tasks. In \cite{alanwarPrOLocResilientLocalization2017}, homomorphic encryption is used to make time-independent model-free location estimates where an estimator cannot learn sensor measurements or locations. In \cite{aristovEncryptedMultisensorInformation2018}, similar secrecy is achieved with a linear Kalman filter when a hierarchical sensor network is present. In \cite{shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013}, privacy-preserving aggregation schemes are presented as a means to compute total powergrid usage without disclosing individual contributions, while in \cite{alexandruEncryptedCooperativeControl2019,alexandruPrivateWeightedSum2020}, centralised and hidden weighted sum aggregations, pWSAc and pWSAh, are introduced as a means for computing local control inputs in a distributed environment without learning individual inputs.

Our contribution in this work presents a range-only localisation method meeting formal cryptographic requirements that ensure sensors keep their measurements, sensor variances and locations private while the navigator keeps its estimates private. We first define a novel notion for private linear combination aggregation and present an implementation that satisfies these requirements, before using it to derive a filter based on the Extended Kalman Filter with no hierarchical sensor layout assumptions. The linear combination aggregation scheme we put forward is in principle similar to the pWSAh scheme in \cite{alexandruPrivateWeightedSum2020}, however, a formal definition with different communication assumptions and leakages is given, crucial for its cryptographic security. To the best of the authors' knowledge, no existing method for Bayesian state estimation using range-only sensors and meeting the desired privacy requirements exists.

We motivate this scenario with the example of vehicle localisation in the presence of privately owned measurement stations. While the intention of measurement stations is the accurate navigation of passing vehicles, it may be reasonable to desire identifying details, such as hardware specifications or physical locations, to remain unknown to the other present stations and the navigator. Similarly, a navigator may not wish to disclose their most accurate location estimates to untrusted third-party measurers.

@@

\section{Problem Statement} \label{sec:problem_statement}
In this work, we consider the context of privacy-preserving range sensor navigation, where we want no sensor to learn information about the navigator or other sensors beyond their local measurements, and the navigator to learn no information about individual sensors beyond its location estimate. The problem is two-fold, in that we require explicit cryptographic requirements with a suitable encryption scheme meeting them, as well as an estimation scheme that can use the encryption in the context of range-only navigation.

@@

As aggregation is typically performed on scalar inputs, we extend our notation to the context of multidimensional estimation data by letting an instance $t_{k,\tau}$ uniquely capture the scalar aggregation during an estimation timestep $k$ for a single element with position index $\tau$. To achieve this in practice, any injective function can be used, such as the concatenation $t_{k,\tau}=k\mathbin\|\tau$. The four algorithms defining our scheme are given as follows.
\begin{LaTeXdescription}
    \item[$\mathsf{Setup}(\kappa)$] On input parameter $\kappa$, generate two equal-length, sufficiently large, primes $p$ and $q$, and compute $N=pq$. Define a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$, choose the number of weights to combine, $m>1$, and set public parameter $\mathsf{pub}=H$, navigator public key $pk_0 = N$ and navigator private key $sk_0=(p,q)$. Sensor secret keys are generated by choosing $sk_i,\,i\in\{1,\dots,n-1\}$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key as $sk_n = -\sum^{n-1}_{i=1}sk_i \pmod{N^2}$.
